Jeff Goldsmith

### 2018-07-23 index.Rmd
update papers; new teaching list; change office number

Jeff Goldsmith  
[Department of Biostatistics](http://www.mailman.columbia.edu/academic-departments/biostatistics)  
[Columbia Mailman School of Public Health](http://www.mailman.columbia.edu/)  
722 West 168th Street, Room 630  
New York, New York 10032

>>>>

Jeff Goldsmith  
[Department of Biostatistics](http://www.mailman.columbia.edu/academic-departments/biostatistics)  
[Columbia Mailman School of Public Health](http://www.mailman.columbia.edu/)  
722 West 168th Street, Room 617  
New York, New York 10032

### 2018-07-23 papers.Rmd
updating subpage stylesheets so academicons work throughout
update papers list and CV
update papers; new teaching list; change office number

>>>>

J. A. Woo Baidal, K. Morel, K. Nichols, E. Elbel, N. Charles, **J. Goldsmith**, L. Chen, and E. M. Taveras (2018+). 
Sugar-sweetened beverage attitudes and consumption during the first 1,000 days of life. 
<i> American Journal of Public Health, </i> 
accepted.

J. Wrobel<sup>&#8225;</sup>, V. Zipunnikov, J. Schrack, and **J. Goldsmith** (2018+).
Registration for exponential family functional data.
<i> Biometrics, </i> 
accepted.

Y. Chen<sup>&#8225;</sup>, **J. Goldsmith**, and R. T. Ogden (2018+).
Functional data analysis of dynamic PET data.
<i> Journal of the American Statistical Association, </i> 
accepted.

Y. Chen<sup>&#8225;</sup>, **J. Goldsmith**, and R. T. Ogden (2018+).
Nonlinear mixed-effects models for PET data.
<i> Transactions on Biomedical Engineering, </i> 
accepted.

### 2018-07-23 teaching.Rmd
updating subpage stylesheets so academicons work throughout
update papers; new teaching list; change office number

Fall 2017: [Data Science I](http://jeffgoldsmith.com/DSI/)

@@

Spring 2016: [Linear Regression Models](http://jeffgoldsmith.com/P8111/)  
Spring 2015: Linear Regression Models  
Summer 2015: Applied Regression II  
Spring 2014: Linear Regression Models  
Spring 2014: Categorical Data Analysis  
Spring 2013: Linear Regression Models  
Spring 2013: Categorical Data Analysis

>>>>

Fall 2018: [Data Science I](http://p8105.com)

@@

Fall 2017: Data Science I
Spring 2016: [Linear Regression Models](http://jeffgoldsmith.com/P8111/)  
Spring 2015: Linear Regression Models  
Summer 2015: Applied Regression II  
Spring 2014: Linear Regression Models  
Spring 2014: Categorical Data Analysis  
Spring 2013: Linear Regression Models  
Spring 2013: Categorical Data Analysis
